Milestone 7

### 2020-04-29 Draft_1.Rmd
filtering by population cutoffs

@trounstine_segregation_2016 suggests that high levels of residential segregation are associated with increased political polarization and decreased public spending. In this analysis, I was able to successfully replicate @trounstine_segregation_2016’s main results. Adding onto her original analysis, I impute a large amount of missing data from the original dataset and re-run the analysis. Finally, I add in income segregation as a predictor in her regressions to assess whether this could be a confounding variable.

@@

fin_imp <- fin_imp %>%
  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp, pctasianpopinterp,
         pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100, pctrentersinterp, pctover65,
         pctcollegegradinterp, logpop, geo_id2, chng5pctblk, chng5pctlatino, chng5pctasian,
         ideology_fill, totaltractsf)

@@

```{r fp_imputations, include = FALSE}

@@

ini <- mice(fin_imp, maxit=0, print=F)

@@

imp_fs <- mice(fin_imp, method = meth, maxit = 5)

@@

head(complete(imp_fs))

@@

@@

```{r new_imp}

@@

miss_var_summary(complete(new_imp_fs))
```

@@

@@

>>>>

@trounstine_segregation_2016 suggests that high levels of residential segregation are associated with increased political polarization and decreased public spending. In this analysis, I was able to successfully replicate @trounstine_segregation_2016’s main results. Adding onto her original analysis, I impute a large amount of missing data from the original dataset and re-run the analysis.

@@

fin_imp <- fin_imp %>%
  select(H_citytract_NHW_i, dgepercap_cpi, diversityinterp, pctblkpopinterp,
         pctasianpopinterp,pctlatinopopinterp, medinc_cpi, pctlocalgovworker_100,
         pctrentersinterp, pctover65, pctcollegegradinterp, logpop, geo_id2,
         chng5pctblk, chng5pctlatino, chng5pctasian, ideology_fill)

# When we subset for only the cities in the original analysis, this about doubles the sample size still...

fin_imp_cities <- fin_imp %>%
  filter(geo_id2 %in% cities_trounstine_fp)

@@

```{r fp_imputations_original, include = FALSE}

@@

ini <- mice(fin_imp, maxit = 0, print = FALSE)

@@

imp_fs <- mice(fin_imp, method = meth, maxit = 1)

imp_fs_all <- mice(fin_imp, method = "cart", maxit = 5)

@@

@@

282334 - 222957

@@

```{r}
#now missing 282261

#before impute:
```

```{r new_imp_less_than_17_nas}

@@

miss_var_summary(complete(new_imp_fs))

```{r fp_imputations_cities, include = FALSE}

ini <- mice(fin_imp_cities, maxit = 0, print = FALSE)

imp_fs_cities <- mice(fin_imp_cities, method = meth, maxit = 1)

fit_imp_felm1 <- with(imp_fs_cities, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r fp_population_full_range}

# what if we condition on population size?

fin_imp_pop_size <- fin_imp %>%
  filter(logpop > 6 & logpop < 16)

nrow(fin_imp_pop_size)

ini <- mice(fin_imp_pop_size, maxit = 0, print = FALSE)

imp_fs_pop_size <- mice(fin_imp_pop_size, method = meth, maxit = 5)

fit_imp_felm1 <- with(imp_fs_pop_size, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r 95_pop}
fin_imp_pop_trounstine_95 <- fin_imp %>%
  filter(logpop < 11.93437 & logpop > 8.7754)

nrow(fin_imp_pop_trounstine_95)

ini <- mice(fin_imp_pop_trounstine_95, maxit = 0, print = FALSE)

imp_fs_pop_size_trounstine_95 <- mice(fin_imp_pop_trounstine_95, method = meth, maxit = 5)

fit_imp_felm1 <- with(imp_fs_pop_size_trounstine_95, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r fp_population_full_range}

# what if we condition on population size?

fin_imp_pop_size <- fin_imp %>%
  filter(logpop > 6 & logpop < 16)

nrow(fin_imp_pop_size)

ini <- mice(fin_imp_pop_size, maxit = 0, print = FALSE)

imp_fs_pop_size <- mice(fin_imp_pop_size, method = meth, maxit = 5)

fit_imp_felm1 <- with(imp_fs_pop_size, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_first_quartile}

quantile(fin_dge$logpop, c(.25))

quantile(fin_seg$logpop, c(.25), na.rm = T)

fin_imp_pop_trounstine_first_quart <- fin_imp %>%
  filter(logpop < 9.388152)

nrow(fin_imp_pop_trounstine_first_quart)

gg_miss_var(fin_imp_pop_trounstine_first_quart, show_pct = T)

ini <- mice(fin_imp_pop_trounstine_first_quart, maxit = 0, print = FALSE)

imp_fs_pop_size_bottom_25 <- mice(fin_imp_pop_trounstine_first_quart, method = meth, maxit = 5)

fit_imp_felm1 <- with(imp_fs_pop_size_bottom_25, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_top_90_trounstine}

quantile(fin_dge$logpop, c(.90))

quantile(fin_seg$logpop, c(.90), na.rm = T)

fin_imp_pop_top_90_trounstine <- fin_imp %>%
  filter(logpop > 11.43575)

nrow(fin_imp_pop_top_90_trounstine)

gg_miss_var(fin_imp_pop_top_90_trounstine, show_pct = T)

ini <- mice(fin_imp_pop_top_90_trounstine, maxit = 0, print = FALSE)

imp_fs_pop_size_top_90_trounstine <- mice(fin_imp_pop_top_90_trounstine, method = meth, maxit = 5)

fit_imp_felm1 <- with(imp_fs_pop_size_top_90_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_bottom_5_trounstine}

quantile(fin_dge$logpop, c(.05))

quantile(fin_seg$logpop, c(.05), na.rm = T)

fin_imp_pop_bottom_5_trounstine <- fin_imp %>%
  filter(logpop < 8.775581)

nrow(fin_imp_pop_bottom_5_trounstine)

gg_miss_var(fin_imp_pop_bottom_5_trounstine, show_pct = T)

ini <- mice(fin_imp_pop_bottom_5_trounstine, maxit = 0, print = FALSE)

imp_fs_pop_size_bottom_5_trounstine <- mice(fin_imp_pop_bottom_5_trounstine, method = meth, maxit = 1)

fit_imp_felm1 <- with(imp_fs_pop_size_bottom_5_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_pop_size_bottom_5_trounstine))

miss_var_summary(fin_imp_cities)

nrow(complete(imp_fs_pop_size_bottom_5_trounstine))

5039 - 4966

```{r population_bottom_1}

quantile(fin_dge$logpop, c(.01))

quantile(fin_seg$logpop, c(.20), na.rm = T)

fin_imp_pop_bottom_1_trounstine <- fin_imp %>%
  filter(logpop < 8.364976 )

nrow(fin_imp_pop_bottom_1_trounstine)

gg_miss_var(fin_imp_pop_bottom_1_trounstine, show_pct = T)

ini <- mice(fin_imp_pop_bottom_1_trounstine, maxit = 0, print = FALSE)

imp_fs_pop_size_bottom_1_trounstine <- mice(fin_imp_pop_bottom_1_trounstine, method = meth, maxit = 1)

fit_imp_felm1 <- with(imp_fs_pop_size_bottom_1_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_over_Baqir}

# Baqir et al uses city as population above 25,000

baqir <- log(25000)

fin_imp_pop_over_baqir <- fin_imp %>%
  filter(logpop > baqir )

nrow(fin_imp_pop_over_baqir)

gg_miss_var(fin_imp_pop_over_baqir, show_pct = T)

ini <- mice(fin_imp_pop_over_baqir, maxit = 0, print = FALSE)

imp_fs_pop_overbaqir <- mice(fin_imp_pop_over_baqir, method = meth, maxit = 5)

fit_imp_felm1 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_under_Baqir}

# Baqir et al uses city as population above 25,000

baqir <- log(25000)

fin_imp_pop_under_baqir <- fin_imp %>%
  filter(logpop < baqir )

nrow(fin_imp_pop_under_baqir)

gg_miss_var(fin_imp_pop_under_baqir, show_pct = T)

ini <- mice(fin_imp_pop_under_baqir, maxit = 0, print = FALSE)

imp_fs_pop_under_baqir <- mice(fin_imp_pop_under_baqir, method = meth, maxit = 1)

fit_imp_felm1 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_mid_50}

# essentially the same - let's do full population
(quantile(fin_seg$logpop, c(.25, .75), na.rm = T))
(quantile(fin_imp$logpop, c(.25, .75), na.rm = T))

baqir <- log(25000)

fin_imp_pop_mid_50 <- fin_imp %>%
  filter(logpop > 5.777652 & logpop < 7.936303)

nrow(fin_imp_pop_mid_50)

gg_miss_var(fin_imp_pop_mid_50, show_pct = T)

ini <- mice(fin_imp_pop_mid_50, maxit = 0, print = FALSE)

imp_fs_pop_mid_50 <- mice(fin_imp_pop_mid_50, method = meth, maxit = 1)

fit_imp_felm1 <- with(imp_fs_pop_mid_50, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_top_1_trounstine}

(quantile(fin_seg$logpop, c(.99), na.rm = T))
(quantile(fin_dge$logpop, c(.99), na.rm = T))

fin_imp_top_1_trounstine <- fin_imp %>%
  filter(logpop > 13.1907 )

nrow(fin_imp_top_1_trounstine)

gg_miss_var(fin_imp_top_1_trounstine, show_pct = T)

ini <- mice(fin_imp_top_1_trounstine, maxit = 0, print = FALSE)

imp_fs_pop_top_1_trounstine <- mice(fin_imp_top_1_trounstine, method = meth, maxit = 5)

fit_imp_felm1 <- with(imp_fs_pop_top_1_trounstine, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

nrow(complete(imp_fs_pop_top_1_trounstine))

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

```{r population_top_1}

(quantile(fin_seg$logpop, c(.99), na.rm = T))
(quantile(fin_dge$logpop, c(.99), na.rm = T))

fin_imp_top_1 <- fin_imp %>%
  filter(logpop > 11.28648)

nrow(fin_imp_top_1)

gg_miss_var(fin_imp_top_1, show_pct = T)

ini <- mice(fin_imp_top_1, maxit = 0, print = FALSE)

imp_fs_pop_top_1 <- mice(fin_imp_top_1_trounstine, method = meth, maxit = 5)

fit_imp_felm1 <- with(imp_fs_pop_top_1, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

# RESULTS ARE ESSENTIALLY THE SAME!
print(imp_felm1_sum)

nrow(complete(imp_fs_pop_top_1))

# doesn't add very much to the sample though, still, robust to additional 73 entries

miss_var_summary(complete(imp_fs_cities))

miss_var_summary(fin_imp_cities)

5039 - 4966

@@

print(imp_felm1_sum)

@@

# cities in original Trounstine

cities_trounstine_fp <- fin_dge %>%
  select(geo_id2) %>%
  unique() %>%
  pull()

# pop quantiles original Trounstine

quantile(fin_dge$logpop, c(.10, .25, .5, .75, .90))

quantile(fin_dge$logpop, c(.05, .95))

nrow(fin_imp)

fin_imp_pop_trounstine_95 <- fin_imp %>%
  filter(logpop < 11.93437 & logpop > 8.7754)
